\documentclass[letterpaper,11pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp---evaluated tools, authored a white paper, rolled out probes + ServiceNow alerts---saving \$120K/yr and raising critical portal uptime to 99.9\%.}
        \resumeItem{Automated RCA follow-ups with a C\# parser extracting action items from outage docs, building a live Excel tracker, and pushing tasks via REST API to ServiceNow.}
        \resumeItem{Collaborated directly with customer stakeholders to validate requirements and gather feedback; authored technical documentation and presented findings.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two open-source wildlife-tracking projects (20+ students), driving end-to-end delivery on Linux and participating in sprint ceremonies, code reviews, and design discussions.}
        \resumeItem{Built cross-platform Python/C++ packages with GitHub Actions CI/CD; validated requirements with external partners and coordinated deliverables across rotating teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Automated requirements traceability with a Python + DXL tool pulling DOORS requirements and TestRail results into a live matrix, cutting a month of manual work to 30 minutes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Papyrus}{}
      {AI-powered data product with similarity search and NLG}{Apr 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Built a RAG research assistant with a FastAPI + Python backend performing similarity search over academic PDFs via sentence-transformer embeddings and Qdrant vector search.}
        \resumeItem{Developed a React/Next.js frontend with streaming chat, citation visualization, and natural-language generation; containerized with Docker Compose for Linux deployment.}
      \resumeItemListEnd

    \resumeSubheading
      {Claude Code MCP Servers \& Tasque Manager}{}
      {Claude Code agentic tool integrations and orchestration}{Mar 2026 -- Apr 2026}
      \resumeItemListStart
        \resumeItem{Built and published 7 TypeScript MCP servers (200+ tools) extending \textbf{Claude Code} with external service access for agentic AI workflows across education, finance, communication, and health.}
        \resumeItem{Built a Claude Code task orchestration daemon that schedules AI-driven jobs on cron, delivers structured results via Discord, and integrates the full MCP tool ecosystem.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages \& AI/ML}{: Python, Java, TypeScript/JavaScript, C/C++, SQL, PyTorch, scikit-learn, LangChain, LLMs (Claude, GPT), RAG}
   }
   \item{
     \textbf{Web \& Tools}{: React, Next.js, FastAPI, Node.js, Docker, Linux, Git, GitHub Actions, Claude Code, Qdrant, FAISS}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
