\documentclass[letterpaper,11pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two embedded wildlife-tracking projects (20+ students), driving end-to-end delivery across PCB-level hardware, firmware, DSP, and Linux ground tooling.}
        \resumeItem{Delivered tower power-system analysis and technical documentation, including an energy budget, solar sizing from irradiance data, and LTspice hot-swap safety simulations.}
        \resumeItem{Built a unified SDR/DSP stack (Python + C++ via pybind11) interfacing with USRP B200mini, AirSpy, and HackRF hardware; validated signal integrity with oscilloscopes and spectrum analyzers during field bring-up.}
        \resumeItem{Implemented a framed-protobuf control link with CRC, ACK/retry, and connection-quality metrics; added hardware-free simulator modes to enable rapid iteration before hardware was available.}
      \resumeItemListEnd

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp---evaluated tools, authored a finance-backed white paper, rolled out probes + ServiceNow alerts---saving \$120K/yr and raising critical portal uptime to 99.9\%.}
        \resumeItem{Authored formal technical reports and test protocols; automated RCA follow-ups with a C\# parser building a live Excel tracker pushed via REST API to ServiceNow.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Automated requirements traceability with a Python + DXL tool pulling DOORS requirements and TestRail verification results into a live matrix, cutting a month of manual work to 30 minutes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FollowMe Robot}{}
      {Bluetooth direction-finding hardware/firmware stack}{Apr 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Built a BLE direction-finding ``follow-me'' hardware stack using angle-of-arrival + RSSI ranging on Silicon Labs NCP modules to estimate 3D tag position in real time.}
        \resumeItem{Implemented the embedded host pipeline in C (NCP/BGAPI ingest, AoA solve, spherical-to-Cartesian); validated with oscilloscope and published pose telemetry over MQTT into ROS.}
        \resumeItem{Submitted manuscript to IEEE/ASME International Conference on Advanced Intelligent Mechatronics.}
      \resumeItemListEnd

    \resumeSubheading
      {RoboCup SSL Robot Runtime}{}
      {Raspberry Pi + STM32 runtime for omni-drive control}{Sep 2022 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Built a Raspberry Pi runtime that decodes Protobuf commands and converts velocity targets into 4-wheel omni-drive RPM setpoints, streamed to an STM32 controller over UART.}
        \resumeItem{Bench-debugged UART timing and telemetry framing using oscilloscopes and multimeters; added analytics tooling to plot expected vs.\ actual wheel velocities for tuning and PCB bring-up.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Hardware}{: Altium (coursework), LTspice, oscilloscopes, multimeters, signal analyzers, soldering, PCB bring-up, STM32, Raspberry Pi, BLE/NCP}
   }
   \item{
     \textbf{Embedded \& Tools}{: C, C++, Python, SystemVerilog, Bash, Git, Linux, UART, Protobuf, MQTT, MS Office}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
