\documentclass[letterpaper,10pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UC San Diego Advanced Robotics and Controls Lab}{La Jolla, CA}
      {Graduate Student Researcher}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a real-time monocular SLAM pipeline for in-body 3D reconstruction (kidney/bladder) to enable autonomous sensor-guided steering of a flexible surgical robot.}
        \resumeItem{Built a real-time robotic simulation pipeline in NVIDIA Isaac Sim with physics-based collision modeling and camera pose supervision to validate sensing and navigation algorithms.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking projects and mentored rotating student teams (5--15 active; 20+ total) building low-cost sensor-based monitoring systems, driving end-to-end delivery across sensing hardware, onboard compute, and DSP pipelines.}
      \resumeItemListEnd

      \resumeSubSubheading
        {Radio Telemetry Tracker}{Dec 2024 -- Oct 2025}
        \resumeItemListStart
          \resumeItem{Modernized a drone-based VHF wildlife radio-telemetry platform using SDR (USRP B200mini) to digitize, filter, and process OOK transmitter signals in the 138--235\,MHz band.}
          \resumeItem{Built an OOK ping detector using FFT-based channelization, dynamic thresholding, and width/SNR gating; produced raw IQ captures and CSV ping logs for reproducible offline analysis.}
          \resumeItem{Implemented RSSI-based transmitter localization with a path-loss model and SciPy least-squares optimization, achieving $\sim$1\,m field-validated accuracy.}
          \resumeItem{Added multi-SDR hardware support (USRP B200mini, AirSpy, HackRF) behind a shared interface with consistent buffering, timestamping, and lifecycle controls.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FollowMe Robot}{}
      {Bluetooth direction-finding for Boston Dynamics Spot}{Apr 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Built a BLE direction-finding system using angle-of-arrival estimation on a 4$\times$4 dual-polarized antenna array with RSSI-based ranging for real-time 3D tag tracking.}
        \resumeItem{Implemented the host pipeline in C (NCP/BGAPI ingest $\to$ IQ-based AoA solve $\to$ spherical-to-Cartesian conversion) and published telemetry over MQTT.}
        \resumeItem{Integrated tracking into ROS with filtering (averaging, outlier rejection, exponential smoothing) to stabilize localization under multipath and RF noise; submitted manuscript to IEEE/ASME AIM.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------COURSEWORK-----------------
\section{Coursework}
  \resumeSubHeadingListStart

    \resumeCourseheading
      {Parallel Computation}{Sep 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Hand-tuned DGEMM on AWS Graviton3 with cache-blocking + packed panels and ARM SVE microkernel; built high-performance GPU GEMM in CUDA on NVIDIA T4 with shared-memory tiling achieving $\sim$4.8\,TFLOP/s.}
        \resumeItem{Distributed 2D stencil/wave simulator on SDSC Expanse using MPI: 2D domain decomposition, nonblocking halo exchange, and global reductions; strong scaling to hundreds of cores.}
      \resumeItemListEnd

    \resumeCourseheading
      {Digital Systems Laboratory}{Jul 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Designed and simulated digital hardware in SystemVerilog: microcoded datapath + control units, timing-constrained FSMs, LFSR stream ciphers, and modular counter/register-file systems with self-checking testbenches.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C/C++, MATLAB, SystemVerilog}
     \hfill
     \textbf{DSP/Math}{: FFT/IFFT, filtering, transfer functions, linear algebra, probability/statistics}
   }
   \item{
     \textbf{Hardware \& Tools}{: SDR (USRP B200mini), LTspice, DAC/ADC systems, RF front-ends (LNA, antennas), GPS/IMU}
     \hfill
     \textbf{Software}{: NumPy/SciPy, CUDA, MPI, ROS, Git, Linux}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
