\documentclass[letterpaper,11pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UC San Diego Advanced Robotics and Controls Lab}{La Jolla, CA}
      {Graduate Student Researcher}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a real-time monocular SLAM pipeline for in-body 3D reconstruction to autonomously steer a flexible surgical robot; built a simulation pipeline in NVIDIA Isaac Sim with physics-based collision modeling.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking projects and mentored rotating student teams (5--15 active; 20+ total), driving end-to-end delivery across sensing hardware, onboard compute, DSP pipelines, and field-ready ground tooling.}
      \resumeItemListEnd

      \resumeSubSubheading
        {Radio Telemetry Tracker}{Dec 2024 -- Oct 2025}
        \resumeItemListStart
          \resumeItem{Modernized a drone-based wildlife radio-telemetry platform; implemented a Python/C++ DSP stack (pybind11, FFTW, Boost) with FFT-based channelization, dynamic thresholding, and RSSI-based localization via SciPy optimization.}
          \resumeItem{Delivered tower power-system analysis: energy budget, solar sizing from irradiance data, and LTspice hot-swap safety simulations.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FollowMe Robot}{}
      {Bluetooth direction-finding for Boston Dynamics Spot}{Apr 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Built a BLE angle-of-arrival + RSSI ranging stack in C for real-time 3D tag tracking on Boston Dynamics Spot; published pose telemetry over MQTT and integrated into ROS with filtering for multipath rejection.}
      \resumeItemListEnd

    \resumeSubheading
      {RoboCup SSL Robot Runtime}{}
      {Raspberry Pi runtime for omni-drive robot control}{Sep 2022 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Built a Raspberry Pi runtime decoding Protobuf UDP commands into 4-wheel omni-drive RPM setpoints; streamed motor commands to an STM32 over UART with telemetry parsing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------COURSEWORK-----------------
\section{Coursework}
  \resumeSubHeadingListStart

    \resumeCourseheading
      {Introduction to Robotics}{Sep 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Programmed a skid-steer rover in ROS 2: waypoint-following controller, vision-based closed-loop localization, EKF-SLAM for joint trajectory + landmark estimation, and motion planning in an obstacle field.}
      \resumeItemListEnd

    \resumeCourseheading
      {Parallel Computation}{Sep 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Hand-tuned DGEMM on AWS Graviton3 (ARM SVE); GPU GEMM with CUDA achieving $\sim$4.8 TFLOP/s; distributed 2D wave simulator on SDSC Expanse using MPI with 2D domain decomposition and nonblocking halo exchange.}
      \resumeItemListEnd

    \resumeCourseheading
      {Digital Systems Laboratory}{Jul 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Designed and simulated digital hardware in SystemVerilog: datapaths, control units, timed FSMs, and full systems (microcoded multiplier, LFSR stream cipher); validated with self-checking testbenches.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C/C++, SystemVerilog, MATLAB, SQL}
   }
   \item{
     \textbf{Tools \& Platforms}{: ROS/ROS 2, NVIDIA Isaac Sim, LTspice, CUDA, MPI, Git, Linux, GitHub Actions CI/CD, AWS}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
