\documentclass[letterpaper,10pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science; GPA: 3.4}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp: evaluated observability tools, authored a finance-backed white paper, and deployed probes + ServiceNow alert integrations---saving \$120K/year and raising critical portal uptime to 99.9\%.}
        \resumeItem{Built dashboards and reporting workflows to visualize system health metrics, enabling the operations team to identify performance trends and respond proactively to incidents.}
        \resumeItem{Automated ATF-mandated RCA follow-ups with a C\# parser that extracts action items from outage docs, builds a live Excel status tracker, and pushes tasks via REST to ServiceNow.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking projects and mentored rotating student teams (5--15 active; 20+ total), driving end-to-end delivery across data pipelines, signal processing, and field-ready tooling.}
        \resumeItem{Built a Python/C++ DSP stack for real-time SDR signal processing with data validation, logging, and automated quality checks; benchmarked aerial-video detection baselines with reproducible hyperparameter search.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Streamlined analytics for the San Francisco Clipper Card back office via parameterized SQL scripts, enabling clients to resolve 80\%+ of recurring data requests instantly.}
        \resumeItem{Automated requirements traceability with a Python + DXL tool that pulls DOORS requirements and TestRail results into a live matrix, cutting $\sim$1 month of manual cross-checking to $\sim$30 minutes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Music Genre Predictor}{}
      {Multi-class genre classifier}{Sep 2024 -- Dec 2024}
      \resumeItemListStart
        \resumeItem{Built an end-to-end multi-class genre classifier on a Spotify audio-feature dataset (15,150 tracks, 19 genres), including EDA, feature engineering, model selection, and evaluation.}
        \resumeItem{Addressed class imbalance with SMOTETomek, applied log transforms and standardized scaling, tuned models with GridSearchCV, and selected a soft-voting ensemble; analyzed per-genre precision/recall via confusion matrices.}
      \resumeItemListEnd

    \resumeSubheading
      {Jackdaw}{}
      {Balatro simulator for reinforcement learning research}{Mar 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Built a complete Python reimplementation of the Balatro game engine ($\sim$30 modules, 150 joker effects) exposed as a Gymnasium-compatible RL environment; designed 235-dimensional observations with a factored action space and trained agents using Stable-Baselines3 MaskablePPO.}
      \resumeItemListEnd

    \resumeSubheading
      {Basic Needs Center Study}{}
      {Food insecurity research at UCSD}{Jan 2024 -- Mar 2024}
      \resumeItemListStart
        \resumeItem{Analyzed UCOP Basic Needs Dashboard trends alongside a custom UCSD survey (n=116, 22 variables); cleaned and standardized inconsistent schemas across years and merged datasets for subgroup comparisons.}
        \resumeItem{Built EDA dashboards and quantified relationships with Pearson correlations, presenting findings to technical and non-technical audiences.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Data Science \& ML}{: Python, SQL, scikit-learn, NumPy, SciPy, Pandas, PyTorch, Jupyter, regression, classification, clustering, EDA}
   }
   \item{
     \textbf{Visualization \& Tools}{: Dashboards, Matplotlib, data storytelling, Git, Docker, AWS (EC2), Linux, ServiceNow}
   }
   \item{
     \textbf{Coursework}{: Recommender Systems \& Web Mining, Statistical NLP, Probabilistic Reasoning \& Learning}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
