\documentclass[letterpaper,10pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science; GPA: 3.4}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp: evaluated observability tools, authored a finance-backed white paper, and deployed probes + ServiceNow alert integrations---saving \$120K/year and raising critical portal uptime to 99.9\%.}
        \resumeItem{Configured ServiceNow Incident Management workflows and alert routing rules to automate escalation of critical infrastructure events, reducing mean time to acknowledge from hours to minutes.}
        \resumeItem{Automated ATF-mandated RCA follow-ups with a C\# parser that extracts action items from outage docs, builds a live Excel status tracker, and pushes tasks via REST to ServiceNow.}
        \resumeItem{Built dashboards and reporting workflows to visualize system health metrics, enabling the operations team to identify performance trends and respond proactively to incidents.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking projects and mentored rotating student teams (5--15 active; 20+ total), driving end-to-end delivery across data pipelines, signal processing, and field-ready tooling.}
        \resumeItem{Documented process flows, technical specifications, and onboarding guides for cross-functional teams spanning hardware, firmware, and software disciplines.}
        \resumeItem{Built automated testing and data-validation pipelines with reproducible configurations, improving quality assurance across iterative development cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Automated requirements traceability with a Python + DXL tool that pulls DOORS requirements and TestRail results into a live matrix, cutting $\sim$1 month of manual cross-checking to $\sim$30 minutes.}
        \resumeItem{Streamlined analytics for the San Francisco Clipper Card back office via parameterized SQL scripts, enabling clients to resolve 80\%+ of recurring data requests instantly.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Personal Website}{}
      {Content-driven portfolio site with Eleventy}{Dec 2025 -- Dec 2025}
      \resumeItemListStart
        \resumeItem{Built a content-driven personal site with reusable components, JSON-backed data, and Markdown pages; deployed via GitHub Pages CI/CD pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {Fortune Telling with Panda Express}{}
      {Interactive browser game}{Apr 2023 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Built a browser game in HTML/CSS/JavaScript with data-driven logic and a nutrition calculator; set up GitHub Actions CI for formatting, linting, and unit tests.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------COURSEWORK------------
\section{Coursework}
 \resumeSubHeadingListStart
   \item{
     \textbf{Relevant}{: Computer Security, Software Engineering, Operating Systems, Computer Architecture}
   }
 \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{ServiceNow \& ITSM}{: ServiceNow (Incident, Change, Service Catalog), ITIL best practices, workflow configuration, REST API integration}
   }
   \item{
     \textbf{Languages \& Scripting}{: JavaScript/TypeScript, Python, C\#, SQL, HTML/CSS, C/C++}
   }
   \item{
     \textbf{Tools \& Platforms}{: Git, GitHub Actions CI/CD, Docker, AWS (EC2), Linux, Microsoft 365, ServiceNow}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
