\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemBold}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small\textbf{#1}} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItemBold{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeCourseheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\Huge Tyler Flar} \\ \vspace{4pt}
  \small
  San Diego, CA
  $\;|\;$ \href{tel:+16195693700}{+1-619-569-3700}
  $\;|\;$ \href{mailto:tylerflar@gmail.com}{tylerflar@gmail.com}
  $\;|\;$ \href{https://linkedin.com/in/tylerflar/}{linkedin.com/in/tylerflar}
  $\;|\;$ \href{https://tylerflar.com}{tylerflar.com}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science; GPA: 3.4}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UC San Diego Advanced Robotics and Controls Lab}{La Jolla, CA}
      {Graduate Student Researcher}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developing a real-time monocular SLAM pipeline for in-body 3D reconstruction (kidney/bladder) to enable autonomous sensor-guided steering of a flexible surgical robot.}
        \resumeItem{Built a real-time robotic simulation pipeline in NVIDIA Isaac Sim with physics-based collision modeling and camera pose supervision to validate sensing and navigation algorithms.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking hardware projects and mentored rotating student teams (5--15 active; 20+ total) building low-cost sensor-based monitoring systems, driving end-to-end delivery across sensing hardware, onboard compute, and DSP pipelines.}
      \resumeItemListEnd

      \resumeSubSubheading
        {Radio Telemetry Tracker}{Dec 2024 -- Oct 2025}
        \resumeItemListStart
          \resumeItem{Selected and integrated RF/sensor hardware---USRP B200mini SDR, Nooelec LaNA low-noise amplifier, SparkFun NEO-M9N GPS/compass (I\textsuperscript{2}C/QWIIC), and Intel N100 SBC---onto a DJI Matrice 350 RTK drone for automated OOK VHF wildlife tag detection ($\sim$138--235\,MHz).}
          \resumeItem{Built an OOK ping detector using FFT-based channelization, dynamic thresholding, and width/SNR gating; implemented RSSI-based transmitter localization with a path-loss model and least-squares optimization, achieving $\sim$1\,m field-validated accuracy.}
          \resumeItem{Designed a reliability-focused telemetry link using framed Protobuf packets with CRC-CCITT, acknowledgments/retries, timeouts, and connection-quality metrics over SiK V3 radio hardware.}
          \resumeItem{Delivered power-system analysis and documentation including an energy budget, solar panel sizing from irradiance data, and LTspice hot-swap safety simulations for tower-based deployments.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS & OUTSIDE EXPERIENCE-----------------
\section{Projects \& Outside Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FollowMe Robot}{}
      {Bluetooth direction-finding for Boston Dynamics Spot}{Apr 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Built a BLE direction-finding system for Boston Dynamics Spot using angle-of-arrival estimation on a Silicon Labs EFR32BG22 with a 4$\times$4 dual-polarized antenna array and RSSI-based ranging to track a tag's 3D position in real time.}
        \resumeItem{Implemented the host pipeline in C (NCP/BGAPI ingest $\to$ IQ-based AoA solve $\to$ spherical-to-Cartesian conversion) and published pose and angle telemetry over MQTT.}
        \resumeItem{Integrated the tracking stream into ROS with filtering (averaging, outlier rejection, exponential smoothing) to stabilize localization under multipath and RF noise; submitted manuscript to IEEE/ASME AIM.}
      \resumeItemListEnd

    \resumeSubheading
      {RoboCup SSL Robot Runtime}{}
      {Raspberry Pi runtime for omni-drive robot control}{Sep 2022 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Built a Raspberry Pi runtime that decodes Protobuf UDP multicast commands and converts velocity targets into 4-wheel omni-drive RPM setpoints, streaming motor commands to an STM32 controller over UART at 115200\,baud.}
        \resumeItem{Implemented PWM dribbler control via Linux sysfs, telemetry parsing with header validation and buffer resets, and real-time analytics plotting expected vs.\ actual wheel velocities for tuning and debug.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------COURSEWORK-----------------
\section{Coursework}
  \resumeSubHeadingListStart

    \resumeCourseheading
      {Digital Systems Laboratory}{Jul 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Designed and simulated digital hardware in SystemVerilog: microcoded datapath + control units, timing-constrained FSMs, LFSR stream ciphers, and modular counter/register-file systems with self-checking testbenches.}
      \resumeItemListEnd

    \resumeCourseheading
      {Components \& Design Techniques for Computer Systems}{Jul 2023 -- Aug 2023}
      \resumeItemListStart
        \resumeItem{Boolean algebra, logic minimization (K-maps, SOP/POS), sequential circuit design and analysis (latches, D flip-flops, timing diagrams), and FSM implementation from state diagrams through flip-flop + combinational logic.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
