\documentclass[letterpaper,11pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp---evaluated tools, authored a white paper, rolled out probes + ServiceNow alerts---saving \$120K/yr and raising uptime to 99.9\%.}
        \resumeItem{Automated RCA follow-ups with a C\# parser extracting action items from outage docs, building a live Excel tracker, and pushing tasks via REST API to ServiceNow.}
        \resumeItem{Wrote Python and PowerShell automation scripts to monitor scheduled task execution and process log data across distributed services.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Automated requirements traceability with a Python + DXL tool pulling DOORS requirements and TestRail results into a live matrix, cutting a month of manual work to 30 minutes.}
        \resumeItem{Streamlined Clipper Card back-office analytics via parameterized SQL scripts against Oracle databases, enabling clients to resolve 80\%+ of recurring data requests instantly.}
      \resumeItemListEnd

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two wildlife-tracking projects (20+ students), delivering DSP/computer-vision pipelines and a C++/OpenCV background subtractor for aerial wildlife detection.}
      \resumeItemListEnd

    \resumeSubheading
      {UC San Diego, CSE Department}{La Jolla, CA}
      {Teaching Assistant}{Mar 2024 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Co-taught UCSD's core Algorithms sequence for 100+ students; designed walkthroughs on graphs, greedy/DP, and divide-and-conquer; earned consistently Strongly Positive evaluations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Papyrus}{}
      {Full-stack research assistant with data processing pipeline}{Apr 2026 -- Present}
      \resumeItemListStart
        \resumeItem{Built a FastAPI backend that parses PDF documents, generates sentence-transformer embeddings, and stores/queries vectors in Qdrant for section-specific retrieval.}
        \resumeItem{Developed a Next.js frontend with real-time streaming chat and data visualization; containerized the full stack with Docker Compose.}
      \resumeItemListEnd

    \resumeSubheading
      {Claude Code MCP Servers \& Tasque Manager}{}
      {Backend service integrations and task orchestration}{Mar 2026 -- Apr 2026}
      \resumeItemListStart
        \resumeItem{Built 7 TypeScript backend services (200+ endpoints) integrating external data sources with structured parsing/filtering, plus a cron-based task daemon that monitors execution and delivers results via Discord.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, C/C++, C\#, JavaScript/TypeScript, SQL, PowerShell, Bash}
     \quad
     \textbf{Databases}{: SQL, Oracle, Qdrant}
   }
   \item{
     \textbf{Web}{: Flask, FastAPI, Next.js, React, Node.js, HTML/CSS}
     \quad
     \textbf{Tools}{: Git, SVN, Docker, Linux, GitHub Actions, AWS}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
