\documentclass[letterpaper,11pt]{article}
\input{_preamble}

\begin{document}

\input{_heading}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Master's, Computer Science}{Apr 2025 -- Dec 2026}
    \resumeSubheading
      {University of California -- San Diego}{La Jolla, CA}
      {Bachelor's, Computer Science; GPA: 3.8}{Sep 2021 -- Mar 2025}
  \resumeSubHeadingListEnd


%-----------PROFESSIONAL EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Engineers for Exploration}{La Jolla, CA}
      {Project Lead}{Jan 2023 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Led two embedded wildlife-tracking projects (20+ students), driving end-to-end delivery across embedded firmware, DSP/computer-vision pipelines, and Linux ground tooling.}
        \resumeItem{Built a unified Python SDR/DSP stack backed by C++ (FFTW/Boost/UHD via pybind11) supporting multiple SDR platforms (USRP B200mini, AirSpy, HackRF) behind a shared interface.}
        \resumeItem{Implemented a reliability-focused control link using framed protobuf packets over TCP/IP with CRC, ACK/retry, timeouts, and connection-quality metrics; added hardware-free simulator modes.}
        \resumeItem{Set up GitHub Actions CI/CD for cross-platform Python/C++ packages and delivered tower power-system analysis with LTspice hot-swap safety simulations.}
      \resumeItemListEnd

    \resumeSubheading
      {Leidos}{Remote}
      {Chief Engineer Intern}{May 2025 -- Sep 2025}
      \resumeItemListStart
        \resumeItem{Led a DOJ monitoring revamp---evaluated tools, authored a white paper, rolled out probes + ServiceNow alerts---saving \$120K/yr and raising uptime to 99.9\%.}
        \resumeItem{Automated RCA follow-ups with a C\# parser extracting action items from outage docs, building a live Excel tracker, and pushing tasks via REST API to ServiceNow.}
      \resumeItemListEnd

    \resumeSubheading
      {Cubic Transportation Systems}{San Diego, CA}
      {Systems Engineering Intern}{Jun 2023 -- Sep 2023}
      \resumeItemListStart
        \resumeItem{Automated requirements traceability with a Python + DXL tool pulling DOORS requirements and TestRail results into a live matrix, cutting a month of manual work to 30 minutes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {FollowMe Robot}{}
      {Bluetooth direction-finding for Boston Dynamics Spot}{Apr 2025 -- Jun 2025}
      \resumeItemListStart
        \resumeItem{Built a BLE direction-finding ``follow-me'' stack for Boston Dynamics Spot using angle-of-arrival + RSSI ranging to estimate 3D tag position in real time.}
        \resumeItem{Implemented the host pipeline in C (NCP/BGAPI ingest $\rightarrow$ AoA solve $\rightarrow$ spherical-to-Cartesian) and published pose telemetry over MQTT; integrated into ROS with filtering and outlier rejection.}
        \resumeItem{Submitted manuscript to IEEE/ASME International Conference on Advanced Intelligent Mechatronics.}
      \resumeItemListEnd

    \resumeSubheading
      {RoboCup SSL Robot Runtime}{}
      {Raspberry Pi runtime for omni-drive robot control}{Sep 2022 -- Jun 2023}
      \resumeItemListStart
        \resumeItem{Built a Raspberry Pi runtime that subscribes to AI UDP multicast commands, decodes Protobuf messages, and converts velocity targets into 4-wheel omni-drive RPM setpoints.}
        \resumeItem{Streamed motor commands to an STM32 controller over UART with telemetry receive/parsing, header filtering, and buffer resets.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: C, C++, Python, C\#, Java, JavaScript/TypeScript, Bash}
     \quad
     \textbf{Embedded}{: STM32, Raspberry Pi, UART, BLE, SDR}
   }
   \item{
     \textbf{Systems \& Tools}{: Linux, Docker, Git, GitHub Actions CI/CD, ROS 2, Protobuf, MQTT, TCP/IP, OpenCV, pybind11}
   }
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
